%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Adam Resnick
\documentclass[margin,line]{resume}
\usepackage{comment}
\usepackage{url}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Adam M. Resnick \normalsize \hspace{97mm}  \url{www.adammresnick.com}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    22909 Fern Ave						                           \hfill (650) 458-7866\\
    Torrance, CA 90505								\hfill amresnick@gmail.com

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Stanford University} \hfill \textbf{December, 2015} \\%\vspace{2mm}\\\vspace{1mm}%
    \textsl{MS, Aerospace Engineering} \\%\vspace{-3mm}\\\vspace{-1mm}\\%
    GPA: 3.634

    \textbf{University of California, Berkeley} \hfill \textbf{May, 2012}\\%\vspace{2mm}\\\vspace{1mm}
    \textsl{BS, Mechanical Engineering} \\%\vspace{-3mm} \\\vspace{-1mm}\\%
    GPA: 3.817, Graduated with Honors

    \textbf{Hong Kong University of Science and Technology (HKUST)}\\
    \textsl{Study Abroad} \hfill \textbf{Fall, 2010}\\ \vspace{-5mm}


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Computer\\ Skills}

    \textsl{Languages:} MATLAB/Simulink, C/C++, \LaTeX , Python, Scheme\\
    \textsl{Packages:} Altium, LTSpice, COMSOL, SolidWorks, AutoCAD, DipTrace, Eagle, gEDA%\\
    %\textsl{Operating Systems:} Windows, Linux, OS X


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Experience}

    \textbf{IJK Controls}\\
    \textsl{Controls Engineer} \hfill \textbf{June 2014 - Present}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
        \item Design, layout, routing (in Altium), debugging of rigid/rigid flex mixed signal PCBs for high bandwidth gimbal stabilization and pointing using brushless 3 phase motors
        \item High bandwidth voice coil controller hardware simulation and design modifications
        \item Implementating high performance gimbal control, pointing, and stabilization on TI DSPs in C
    \end{itemize} \vspace{-2.25mm}

    \textbf{Stanford Space Rendezvous Lab}\\
    \textsl{Graduate Student Researcher} \hfill \textbf{Spring, 2014}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
        \item Simulating GPS-based orbit estimation for relative navigation of formation flying satellites
    \end{itemize} \vspace{-2.25mm}

    \textbf{Stanford Autonomous Systems Lab}\\
    \textsl{Graduate Student Researcher} \hfill \textbf{Winter, 2014}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
        \item Investigate global stability of cyclic pursuit control laws for satellite formation flight
    \end{itemize} \vspace{-2.25mm}

    \textbf{NASA Goddard Space Flight Center}\\
    \textsl{Atittude Control Systems Engineering Intern} \hfill \textbf{Summer, 2013}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
        \item Individually designed/built HIL satellite simulator for attitude sensing and estimation systems
        \item Design \& layout of PCBs and a course sun sensor
        \item Allan variance computation to build stochastic models of MEMS gyros
    \end{itemize} \vspace{-2.25mm}

    \textbf{NASA Ames Research Center}\\ %\vspace{2mm}\\\vspace{1mm}%
    \textsl{Undergraduate Student Research Program Intern} \hfill \textbf{Summer, 2012 \& Summer, 2011}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
    	\item Engineer solutions to bring damaged scientific instruments online
    	\item Nano-material characterization using FTIR, Raman and UV/Vis spectroscopy and AFM
        \item Led a team of undergrads in repairing a \$150,000 instrument
        \item Conducted research into dye-sensitized solar cells in Dr. Bin Chen's lab
    \end{itemize} \vspace{-2.25mm}

    %\textbf{Carbon Design Innovations}\\
    %\textsl{Mechanical Engineering Intern} \hfill \textbf{Summer, 2012}\\ \vspace{-4mm}
    %\begin{itemize} \itemsep -2pt
   % 	\item FEA of carbon nanotube-tipped AFM probes
   %  	\item Modeled proprietary CNT processing steps to demonstrate increased probe robustness
   %  	\item Validation of analytical models using an AFM
   % \end{itemize} \vspace{-2.25mm}

    \textbf{5-Axis CNC Airbrush Painting Machine}\\
    \textsl{ME 102B Mechatronics Class} \hfill \textbf{Spring, 2012}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
    	\item $\mu$C code to drive stepper motors, enabling stage movement along any line in 3D-space
    	\item PCB schematic, layout and precise machining of mechanical parts
    \end{itemize} \vspace{-2.25mm}

%    \textbf{NASA Ames Research Center}\\
%    \textsl{Undergraduate Student Research Program} \hfill \textbf{Summer, 2011}\\ \vspace{-4mm}
%    \begin{itemize} \itemsep -2pt
%    	\item Led a team of undergrads in repairing a \$150,000 instrument
%    	\item Conducted research into dye-sensitized solar cells in Dr. Bin Chen's lab
%    \end{itemize} \vspace{-2.25mm}

    \textbf{Magnetic Levitation and Robust Swing-Up Inverted Pendulum}\\
    \textsl{EE 128 Control Systems Class} \hfill \textbf{Fall, 2011}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
    	\item Analog controller designed using system ID, linearization and MATLAB and built in circuitry
        \item Controller design using state feedback and an observer in Simulink with an LQR solution
    \end{itemize} \vspace{-2.25mm}

%    \textbf{UC Berkeley Prof. Liwei Lin's Lab}\\
%    \textsl{Undergraduate Researcher} \hfill \textbf{Feb, 2010 - May, 2011}\\ \vspace{-4mm}
%    \begin{itemize} \itemsep -2pt
%    	\item Investigate which synthesis parameters lead to highest quality nano-materials
%    \end{itemize} \vspace{-2.25mm}

    \textbf{UC Berkeley Solar Vehicle Team}\\
    \textsl{Li-Ion Battery System Mechanical Lead} \hfill \textbf{Jan, 2009 - Summer, 2010}\\ \vspace{-4mm}
    \begin{itemize} \itemsep -2pt
    	\item Led mechanical design and construction from individual cells to complete batteries
    	\item Electrical system integration
    \end{itemize} \vspace{-2.25mm}

%__________________________________________________________________________________________________________________
    %
    % Honours and Awards
    \section{\mysidestyle Honors and\\Awards}

    NSF GRFP Honorable Mention                    \\
    %Student Private Pilot, 7 Hours PIC           \\
    Dean's List, HKUST \vspace{1mm}               \\
    Member, Tau Beta Pi Engineering Honor Society \\

\begin{comment}
%_________________________________________________________________________________________________________________
    %
    % Relevant Undergraduate Coursework
    \section{\mysidestyle Relevant Undergraduate Coursework}

    EE 20N: Structure and Interpretation of Signals and Systems\\
    EE 40: Introduction to Microelectronic Circuits\\
    EE 120: Signals and Systems\\
    EE 126: Probability and Random Processes\\
    EE 127A: Convex Optimization Models and Applications\\
    EE 128: Feedback Control Systems\\
    ME 102B: Mechatronics Design \\
    ME 132: Dynamic Systems and Feedback\\
    ME 135: Design of Microprocessor-Based Mechanical Systems\\

%_________________________________________________________________________________________________________________
    %
    % Relevant Graduate Coursework
    \section{\mysidestyle Relevant Graduate Coursework}

    AA 242A: Classical Dynamics\\
    AA 203: Optimal Control Theory\\
    AA 271A: Dynamics and Control of Spacecraft and Aircraft\\
    AA 272C: Global Positioning Systems\\
    AA 236A: Spacecraft Design\\
    AA 279A: Space Mechanics\\
    CME 204: Partial Differential Equations in Engineering\\
    CS 223A: Introduction to Robotics\\
    ENGR 209A: Analysis and Control of Nonlinear Systems\\
    EE 261: The Fourier Transform and its Applications\\
    EE 263: Introduction to Linear Dynamical Systems\\

%_________________________________________________________________________________________________________________
    %
    % Planned Graduate Coursework
    \section{\mysidestyle Planned Graduate Coursework}

    AA 212: Analysis and Design of Multivariable Feedback Systems\\
    AA 214A: Introduction to Numerical Methods for Engineering\\
    AA 241X: Design, Construction and Testing of Autonomous Aircraft\\
    AA 279B: Advanced Space Mechanics\\
    CS 221: Artificial Intelligence\\
    CS 225A: Experimental Robotics\\
    CS 229: Machine Learning\\
    EE 364A: Convex Optimization I\\
    EE 364B: Convex Optimization II\\


    %__________________________________________________________________________________________________________________
    % Publications & Presentations
    \section{\mysidestyle Selected Publications \& Presentations}

    Resnick, Adam M., Galante, Joeseph, ``A Hardware-in-the-Loop Testbed for Attitude Sensing and Estimation'',
    Nonlinear Adaptive Filter IRAD Summer Final Report, NASA Goddard Space Flight Center, Summer 2013.

    Resnick, Adam M., Galante, Joeseph, ``A Hardware-in-the-Loop Testbed for Attitude Sensing and Estimation'',
    Presented as part of the Attitude Control Systems branch meeting, NASA Goddard Space Flight Center, August, 30, 2013.

    Resnick, Adam M., ``Flexible Materials for Use in Dye Sensitized Solar Cell Electrodes'',
    Presented as part of the Summer Scientific Poster Session, NASA Ames Research Center, August, 20, 2011.

    Paliwal, K.K., Shannon, B.J., Lyons, J.G. and K.K. W\'ojcicki,
    ``Speech-signal-based frequency warping'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 16, No. 4, pp. 319-322, 2009.

\vspace{-2mm}
    Paliwal, K.K. and K.K. W\'ojcicki,
    ``Effect of analysis window duration on speech intelligibility'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 785-788, 2008.

\vspace{-2mm}
    Stark, A.P., W\'ojcicki, K.K., Lyons, J.G. and K.K. Paliwal,
    ``Noise driven short time phase spectrum compensation procedure for speech enhancement'',
    In \textsl{Proc. INTERSPEECH}, pp. 549-552, 2008.

\vspace{-2mm}
    W\'ojcicki, K.K., Milacic, M., Stark, A.P., Lyons, J.G. and K.K. Paliwal,
    ``Exploiting conjugate symmetry of the short-time Fourier spectrum for speech enhancement'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 461-464, 2008.

\vspace{-2mm}
    W\'ojcicki, K.K. and K.K. Paliwal,
    ``Importance of the dynamic range of an analysis window function for phase-only and magnitude-only reconstruction of speech'',
    In \textsl{Proc. ICASSP}, pp. 729-733, 2007.



    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees}
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
\section{\mysidestyle Referees}

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
Professor                               &  Associate Lecturer                       \\
Griffith University                     &  Griffith University                      \\
Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
Researcher                              &  Systems Engineer                         \\
National ICT Australia                  &  Hewlett Packard                          \\
St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
\end{tabular}


\end{comment}
%_____________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
